SciPy - some descriptive title here

### 2018-06-18 scipy-1.0/paper.tex
Drafted a subsection for LowLevelCallable.

\subsection*{Unified bindings to compiled code}
LowLevelCallable

@@

SciPy adopted an official Governance Document on August 3, 2017 (see PR\#6953). In summary,
we have a Benevolant Dictator for Life (BDFL) in Pauli Virtanen, and a (currently) 18
member Steering Council chaired by Ralf Gommers that i.e., decides on who gets commit rights.

SciPy adopted an official Code of Conduct on October 24, 2017 (see PR\#7963), drawing
inspiration from the Apache Foundation Code of Conduct, the Contributor Covenant,
the Jupyter Code of Conduct, and the Open Source Guides - Code of Conduct. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (do not harass or exclude).
We outline a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.

>>>>

\subsection*{Unified bindings to compiled code}
\subsubsection*{LowLevelCallable}
As of SciPy version 0.19, it is possible for users to wrap low-level
functions in a \texttt{scipy.LowLevelCallable()} object that reduces
the overhead for calling compiled C functions directly from Python.
Supported low-level functions include \texttt{PyCapsule} objects,
ctypes function pointers, and cffi function pointers. The low level
function signature must be consistent with the expectations of the
routine it is passed to. For example, the documentation for
\texttt{scipy.ndimage.generic\_filter} defines two acceptable C callback
function signatures that may be used to produce functions that operate
on each element of image data with low overhead. The C code may be
generated using numba or Cython, for example, as long as the function
call signature matches the specifications. Furthermore, it is even
possible to generate a low-level callback function automatically
from a Cython module using \texttt{scipy.LowLevelCallable.from\_cython}.

@@
